String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-13 2023-1-19/sections/conclusion.tex
space adjustment
experiments

%TODO
This work proposes an efficient automata-theoretical approach for solving string constraints with regex-counting and string-length. The approach is based on the idea of encoding counting operators in regular expressions by registers symbolically, instead of unfolding them explicitly. Moreover, this paper proposes an automata-size reduction technique and an under-approximation based solution searching technique to improve the performance. Finally, we use two benchmark suites comprising almost 50,000 instances in total to evaluate the performance of our approach. The experimental results show that our approach can solve more instances than the other solvers, in almost the same speed as the fasted solver. 
For the future work, we plan to investigate symbolic approaches to dealing with nested counting operators.

>>>>

%TODO
This work proposes an efficient automata-theoretical approach for solving RECL constraints, that is, string constraints with regex-counting and string-length. The approach is based on the idea of encoding counting operators in regular expressions by registers symbolically, instead of unfolding them explicitly. Moreover, this paper proposes an automata-size reduction technique and an under-approximation based solution searching technique to improve the performance. Finally, we use two benchmark suites comprising 48,834 instances in total to evaluate the performance of our approach. The experimental results show that our approach can solve more instances than the state-of-the-art best solvers on RECL constraints, with a comparable performance. For the future work, we plan to investigate symbolic approaches to dealing with nested counting operators.

### 2023-05-13 2023-1-19/sections/implementation.tex
space ajustment
section 6
experiments

We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called OSTRICH$^{\rm RECL}$.
Then we do experiments on two benchmark suites, to evaluate the performance of OSTRICH$^{\rm RECL}$. In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.

@@

\subsection{Benchmark suites}

Our experiments utilize two benchmark suites, namely, AutomatArk and RegCoL. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.

@@

\medskip
\noindent
\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite. These constraints are generated by extracting regular expressions with counting operators from \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form 
$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$. We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them.

@@

\subsection{Experiment results}

We evaluated the performance of OSTRICH$^{\rm RECL}$ against the state-of-the-art string constraint solvers, including CVC5 
%(version 1.0.5) 
\cite{cvc5}, Z3seq \cite{z3seq}, Z3-Trau 
%(github commit 1628747) 
\cite{z3trau}, Z3str3
%(github commit 59e9c87) 
\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH\footnote{The name OSTRICH+ was used in~\cite{atva2020}, where nuXmv model checker was called to solve the nonemptiness of CEFA w.r.t. LIA. } 
%(github commit 8297d8d) 
\cite{atva2020}. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory. We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, where the timeout period is set as 60 seconds per instance.

The experiments are designed to answer the following two research questions. 
\begin{description}
\item[Q1] Does OSTRICH$^{\rm RECL}$ solve RECL constraints more efficiently than the state-of-the-art string constraint solvers ?

\item[Q2] Do the size-reduction and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
\end{description}

Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL. The experimental results can be found in Table~\ref{tab:results_all}. From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solvers almost all 48,834 instances, except 145 of them, that is, it solves 48,698 instances correctly, which is 3,994/2,272/24,577/12,832/1,091/7,092 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, OSTRICH$^{\rm RECL}$ is the second fastest solver. More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

@@

\begin{table}[t]
\vspace{-1mm}
\begin{center}
  \import{tables}{table_all.tex}
\end{center}
  \caption{Experiment results for Q1, where the timeout period is 60 seconds}
  \label{tab:results_all}
\vspace{-5mm}
\end{table}

\begin{table}[ht]
\vspace{-3mm}
\begin{center}
  \subimport{tables}{table_heuristic.tex}
\end{center}
  \caption{Experiment results for Q2, where the timeout period is 60 seconds}
  \label{tab:results_heuristics}
\vspace{-5mm}
\end{table}

To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the size-reduction, under-approximation, or both are removed. 
For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both size-reduction and under-approximation techniques are removed, 
OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp. OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the size-reduction (resp. under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
%OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
The experiment results can be found in Table~\ref{tab:results_heuristics}.
From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column). Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ help to solve 19 more sat instances, while reduces the number of solved unsat instances by 3, since under approximation techniques do not help to solve unsat instances.
%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

>>>>

We implement the algorithms in Section~\ref{sec:algorithm} on top of OSTRICH~\cite{ostrich,atva2020}, resulting in a version of OSTRICH called $\ostrichrecl$.
Then we do experiments on two benchmark suites, to evaluate the performance of $\ostrichrecl$. In the sequel, we first describe the two benchmark suites, then present the settings and results of the experiments.

@@

\vspace{-2mm}
\subsection{Benchmark suites}\label{sec:bench}

Our experiments utilize two benchmark suites, namely, RegCoL and AutomatArk. In total, there are 48,834 instances in the two benchmark suites. All the benchmark instances are in SMTLIB2 format.

\medskip
\noindent
\emph{RegCoL benchmark suite.} There are 40,628 RECL constraints in the RegCoL suite. These constraints are generated by extracting regular expressions with counting operators from the open source regex library \cite{regex_lingua_franca,redos_lenka} and constructing for each regular expression $e$ a RECL constraint of the form 
$x \in e \wedge x \in \overline{\Sigma^*(<+ >+'+''+\&)\Sigma^*} \wedge |x| > 10,$   
where $\Sigma^*(<+ >+'+''+\&)\Sigma^*$ is a regular expression that specifies at least one occurrence of special characters $<$, $>$, $'$, $''$, or $\&$, and $\overline{e'}$ denotes the complement of a regular expression $e'$. 
%We would like to remark that there are about 500,000 real-world regular expressions in \cite{regex_lingua_franca,redos_lenka} and regular expressions with counting operators occupy about 8\% of them. 
Moreover, among these 40,628 RECL constraints, only 5\% of them include non-register-representable regexes.

@@

@@

\vspace{-3mm}
\subsection{Experiment results}

We evaluate the performance of $\ostrichrecl$ against the state-of-the-art string constraint solvers, including CVC5 
%(version 1.0.5) 
\cite{cvc5}, Z3seq \cite{z3seq}, Z3-Trau 
%(github commit 1628747) 
\cite{z3trau}, Z3str3
%(github commit 59e9c87) 
\cite{z3str3}, Z3str3RE \cite{z3str3re}, and OSTRICH\footnote{The name OSTRICH+ was used in~\cite{atva2020}, where nuXmv model checker was called to solve the nonemptiness of CEFA w.r.t. LIA. } 
%(github commit 8297d8d) 
\cite{atva2020}, on RegCoL and AutomatArk. All experiments are conducted on CentOS Stream release 8 with 12 Intel(R) Xeon(R) Platinum 8269CY 3.10GHz CPU cores and 190 GB memory. We use the Zaligvinder framework \cite{zaligvinder_2021} to execute the experiments, where the timeout period is set as 60 seconds per instance.

%The experiments are designed to answer the following two research questions. 
%\begin{description}
%\item[Q1] Does OSTRICH$^{\rm RECL}$ solve RECL constraints more efficiently than the state-of-the-art string constraint solvers ?
%
%\item[Q2] Do the size-reduction and under-approximation techniques proposed in Section~\ref{sec:algorithm} indeed improve the performance ?
%\end{description}

\begin{table}[ht]
\vspace{-2mm}
\begin{center}
  \import{tables}{table_regcol.tex}
\end{center}
  \caption{Experiment results on RegCol, with timeout = 60 seconds}
  \label{tab:results_regcol}
\vspace{-5mm}
\end{table}

The experiment results on the RegCol benchmark suite are put in Table~\ref{tab:results_regcol}. 
From Table~\ref{tab:results_regcol}, we can see that $\ostrichrecl$ solvers almost all 40,628 instances, except 106 of them, that is, it solves 40,522 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092 
3,893/2,081/20,483/10,200/1,082/5,505 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that the solvers  Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth\footnote{Although it seems a bit strange to use one solver as the ground truth, this is the practice for string constraint solving, since CVC5 is the most stable string solver at present.}. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, $\ostrichrecl$ is the second fastest solver. More specifically, $\ostrichrecl$ spends 3.02 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.56 seconds per instance.  
Note that Z3-Trau reports ``unknown'' on 21,655 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

\begin{table}[ht]
\vspace{-2mm}
\begin{center}
  \import{tables}{table_automatark.tex}
\end{center}
  \caption{Experiment results on AutomatArk, with timeout = 60 seconds}
  \label{tab:results_automatark}
\vspace{-5mm}
\end{table}

The experiment results on the AutomatArk benchmark suite are put in Table~\ref{tab:results_automatark}. 
From Table~\ref{tab:results_automatark}, we can see that $\ostrichrecl$ solvers almost all 8,215 instances, except 39 of them, that is, it solves 8,176 instances correctly, which is %3,994/2,272/24,577/12,832/1,091/7,092 
101/191/4,094/2,632/9/1,587
more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Still the soundness errors are reported by taking the results of CVC5 as the ground truth.
%Note that Z3-Trau has soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, $\ostrichrecl$ spends 2.49 seconds per instance on average. 
%while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3.49 seconds per instance.  
%Note that Z3-Trau reports ``unknown'' on 2,552 instances, which seems to be mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

In summary, from the results in Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark}, $\ostrichrecl$ solves 48,698 out of 48,834 instances, which is 1,091 more than Z3str3RE, the state-of-the-art best solver on RECL constraints. Moreover, the performance (speed) of $\ostrichrecl$ is comparable to that of Z3str3RE.

%Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL.

@@

%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
\hide{
\begin{table}[ht]
\vspace{-3mm}
\begin{center}
  \subimport{tables}{table_heuristic.tex}
\end{center}
  \caption{Experiment results for Q2, where the timeout period is 60 seconds}
  \label{tab:results_heuristics}
\vspace{-6mm}
\end{table}

To answer Q2, we compare OSTRICH$^{\rm RECL}$ with its three variants, namely, OSTRICH$^{\rm RECL}$ where the size-reduction, under-approximation, or both are removed. 
For convenience, let us use OSTRICH$^{\rm RECL^-}$ to denote the variant of OSTRICH$^{\rm RECL}$ that both size-reduction and under-approximation techniques are removed, 
OSTRICH$^{\rm RECL^-}_{+\rm SR}$ (resp. OSTRICH$^{\rm RECL^-}_{+\rm UA}$) to denote the variant that is obtained by adding the size-reduction (resp. under-approximation) techniques to OSTRICH$^{\rm RECL^-}$.
%OSTRICH$^{\rm RECL}_{\rm -SR}$, OSTRICH$^{\rm RECL}_{\rm -UA}$, OSTRICH$^{\rm RECL}_{\rm -SRUA}$, which remove size-reduction, under-approximation, and both from OSTRICH$^{\rm RECL}$ respectively. 
The experiment results can be found in Table~\ref{tab:results_heuristics}.
From Table~\ref{tab:results_heuristics}, we can see that adding size-reduction techniques help to solve 1,563 more instances and reduce the average time per instance for 46.4\% (see the OSTRICH$^{\rm RECL^-}_{\rm +SR}$ column), while adding under-approximation techniques help to solve 1,476 more instances and reduce the average time per instance for 42.7\% (see the OSTRICH$^{\rm RECL^-}_{\rm +UA}$ column), moreover, adding both help to solve 1,579 more instances and reduce the average time per instance for 46.5\% (see the OSTRICH$^{\rm RECL}$ column). Note that adding under-approximation to OSTRICH$^{\rm RECL^-}_{\rm +SR}$ help to solve 19 more sat instances, while reduces the number of solved unsat instances by 3, since under approximation techniques do not help to solve unsat instances.
}
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%% Q2 removed %%%%%%%%%%%%
%Moreover, adding these techniques also decrease the average time spent in solving each instance considerably.

### 2023-05-13 2023-1-19/sections/introduction.tex
section 6
experiments

Counting (aka repetition) is a convenient feature in regular expressions that count the number of matchings of sub-patterns. For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice. 
Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator. For instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
Counting is a frequently used feature of regular expressions. According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while the other forms of counting occur in more than 20\% of them. Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints that contain at least regular expressions with counting and string-length function.

@@

The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction and under-approximation techniques, entails an efficient algorithm for solving RECL constraints. We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH, called $\ostrichrecl$ for convenience. 
%
Furthermore, we utilize a collection of benchmark suites, which comprise 48,834 RECL constraints in total, to evaluate the performance of $\ostrichrecl$. The collection of benchmark suites includes a widely-used benchmark suite for string constraints, as well as benchmark suites comprising constraints generated from regular expressions in various open source regex libraries. 
%
%Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contain sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators. 
%
The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while the state-of-the-art best solver Z3str3RE on RECL constraints solves only 47,607 instances (where the timeout period is set as 60 seconds). Moreover, while $\ostrichrecl$ solves 1,091 more instances than Z3str3RE, its performance is comparable to Z3str3RE (2.93 versus 1.71 seconds per instance). In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively, with an average time 5.67, 3.49, 5.41, and 8.54 seconds per instance. (See Table~\ref{tab:results_all} for more details.)

At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced. This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, regex-counting was unfolded explicitly. Moreover, in~\cite{atva2020}, the nonemptiness of CEFA w.r.t. LIA formulas was solved by utilizing the nuXmv model checker~\cite{nuxmv}. In contrast, this work solves it by integrating the techniques of Parikh-image computation, automata-size reduction, and under approximation. The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time. (See Table~\ref{tab:results_all}, where OSTRICH denotes the solver in \cite{atva2020}.)

>>>>

Counting (aka repetition) is a convenient feature in regular expressions that count the number of matchings of sub-patterns. For instance, $a^{\{2, 4\}}$ specifies that $a$ occurs at least twice and at most four times, and $a^{\{2, \infty\}}$ specifies that $a$ occurs at least twice. 
Note that Kleene star and Kleene plus operator can be seen as special cases of counting operator. For instance, $a^*$ and $a^+$ are equivalent to $a^{\{0,\infty\}}$ and $a^{\{1,\infty\}}$.
Counting is a frequently used feature of regular expressions. According to the statistics from \cite{CS16}, Kleene star/plus occur in more than 70\% of 1,204 Python projects, while the other forms of counting occur in more than 20\% of them. Therefore, an efficient analysis of string manipulating programs requires efficient solvers for string constraints that contain at least regular expressions with counting\footnote{In the rest of this paper, for clarity, we use counting to denote expressions of the form $e^{\{m, n\}}$ and  $e^{\{m, \infty\}}$, but not $e^*$ or $e^+$.} and string-length function.

@@

The representation of regex-counting and string-length as registers in CEFA, combined with the aforementioned size-reduction and under-approximation techniques, entails an efficient algorithm for solving RECL constraints. We implement the algorithm on top of OSTRICH, resulting in a new version of OSTRICH, called $\ostrichrecl$ for convenience. 
%
Furthermore, we utilize a collection of benchmark suites, which comprise 48,834 RECL constraints in total, to evaluate the performance of $\ostrichrecl$. The collection of benchmark suites includes a widely-used benchmark suite for string constraints, as well as benchmark suites comprising constraints generated from regular expressions in various open source regex libraries. 
%
%Note that in the benchmark suites, we only consider the regexes that contain explicit counting, that is, regexes that contain sub-expressions of the form $e^{\{n, m\}}$, and ignore those that contain only implicit counting operators, that is, $e^*$ or $e^+$, since the state-of-the-art string solvers suffer mainly from the explicit counting operators. 
%
The experiment results show that $\ostrichrecl$ can solve 48,698 out of 48,834 instances, while Z3str3RE, the state-of-the-art best solver on RECL constraints, solves only 47,607 instances (where the timeout period is set as 60 seconds). Moreover, the speed of $\ostrichrecl$ is comparable to that of Z3str3RE. In comparison, CVC5, Z3seq, Z3-Trau, and Z3str3 solve only 44,704, 46,426, 24,121, and 35,866 instances respectively. (See Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark} for more details.)

At last, we would like to clarify the relationship of this work with~\cite{atva2020}, where CEFA was introduced. This work differs from \cite{atva2020} in the following aspects: In \cite{atva2020}, regex-counting was unfolded explicitly. Moreover, in~\cite{atva2020}, the nonemptiness of CEFA w.r.t. LIA formulas was solved by utilizing the nuXmv model checker~\cite{nuxmv}. In contrast, this work solves it by integrating the techniques of Parikh-image computation, automata-size reduction, and under approximation. The experimental results show that our approach solves 7,092 more instances than the solver in~\cite{atva2020} while spending less time. (See Table~\ref{tab:results_regcol} and Table~\ref{tab:results_automatark} for more details, where OSTRICH denotes the solver in \cite{atva2020}.)

### 2023-05-13 2023-1-19/sections/overview.tex
experiments

We determinize $\cB$, apply the minimization algorithm to the resulting deterministic finite automaton (DFA), and obtain a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b). 
Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experiment results show us that they do reduce the sizes of NFA constructed from the regular expressions in practice. (See Table~\ref{tab:results_heuristics}, where adding the size-reduction techniques reduces the running time for 46.4\%.) 
%thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g. $\{a\}, \{b\}, \{c\}, \Sigma \setminus \{a, b, c\}$, in the transitions of $\aut_1 \times \aut_2$.}.
%Then we reinterpret $\cC$ as a CEFA with the acceptance condition $\alpha(r_0, r_1, r_2, r_3)$. 
%Finally, we compute an LIA formula $\psi'(i_1, \cdots, i_6)$ from $\cC$ and reduce the satisfiability of the string constraint in~(\ref{eqn-running}) to the satisfiability of the following existential LIA formula
%\begin{equation}\label{eqn-LIA-reduced}
%\psi'(i_1, \cdots, i_6) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [6]}  i_k v'_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
%\end{equation}
%where $\myvec{v'_{k}}=(v'_{k,1}, v'_{k,2}, v'_{k,3}, v'_{k,4})$ is the vector of updates of registers of the transition $\tau'_k$ for $k \in [6]$.

@@

We implement all the aforementioned techniques on top of OSTRICH, resulting into a solver $\ostrichrecl$. It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art strings solvers cannot solve it within 300 seconds.

>>>>

We determinize $\cB$, apply the minimization algorithm to the resulting deterministic finite automaton (DFA), and obtain a DFA $\cC$, as illustrated in Figure~\ref{fig:overview:product:reduced}(b). 
Note that $\cC$ contains only three states $q''_0, q''_1, q''_2$ and six transitions, while $\cB$ contains four states and eight transitions. 
Although the determinization and minimization may not reduce the sizes of NFA in the worst case, the experiment results show us that they do reduce the sizes of NFA constructed from the regular expressions in practice. 
%(See Table~\ref{tab:results_heuristics}, where adding the size-reduction techniques reduces the running time for 46.4\%.) 
%thus containing much less number of transitions than $\aut_1 \times \aut_2$\footnote{This is the case even if we consider subsets of characters, e.g. $\{a\}, \{b\}, \{c\}, \Sigma \setminus \{a, b, c\}$, in the transitions of $\aut_1 \times \aut_2$.}.
%Then we reinterpret $\cC$ as a CEFA with the acceptance condition $\alpha(r_0, r_1, r_2, r_3)$. 
%Finally, we compute an LIA formula $\psi'(i_1, \cdots, i_6)$ from $\cC$ and reduce the satisfiability of the string constraint in~(\ref{eqn-running}) to the satisfiability of the following existential LIA formula
%\begin{equation}\label{eqn-LIA-reduced}
%\psi'(i_1, \cdots, i_6) \wedge \bigwedge \limits_{0 \le j \le 3} r_j = \sum \limits_{k \in [6]}  i_k v'_{k, j+1} \wedge \alpha(r_0, r_1, r_2, r_3),
%\end{equation}
%where $\myvec{v'_{k}}=(v'_{k,1}, v'_{k,2}, v'_{k,3}, v'_{k,4})$ is the vector of updates of registers of the transition $\tau'_k$ for $k \in [6]$.

@@

We implement all the aforementioned techniques on top of OSTRICH, resulting into a solver $\ostrichrecl$. It turns out that $\ostrichrecl$ is able to solve the string constraint in~(\ref{eqn-running}) within one second, while the state-of-the-art string solvers are incapable of solving it within 300 seconds.
